Data Cleaning

### 2024-02-20 R/processing-code/Cleaning Data/cleaning1.qmd
Uploaded clean1

Save cleaned data as an RDS file.
```{r}
output_file2<- here("data", "processed-data", "NIS_Teen_Data_2022_clean1.csv")
write.csv(NISTeenVax4, file = output_file2, row.names = FALSE)
saveRDS(NISTeenVax4, file = "./data/processed-data/clean_data1.rds")
```

>>>>

Save cleaned data as an RDS file.
```{r}
output_file2<- here("data", "processed-data", "NIS_Teen_Data_2022_clean1.csv")
write.csv(NISTeenVax4, file = output_file2, row.names = FALSE)
saveRDS(NISTeenVax4, file = "./data/processed-data/cleandata1.rds")
```
